### 2022-05-13 main/chapter_2ljets.tex
add exclusion plots

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figures/2ljets_summary_log.pdf}
\caption{%
Data of the $\twoljets$ electroweak analysis with \emph{post-fit} backgrounds
for which the lower panel shows $S_\mathrm{ATLAS}$ from
Equation~\ref{eqn:significance_atlas}.
Control, validation and signal regions are shown from left to right, with the
regions within each category ordered approximately by their typical $\ptmiss$.
The `Top' category contains $t\bar t$ and $tW$ processes, and
`Other' contains fake/non-prompt lepton, higgs, triboson, , $t\bar tZ$ and other
rare top processes.%
}
\label{fig:ewk_summary}
\end{figure}

>>>>

Our central result is Figure~\ref{fig:2ljets_summary}, which shows the names,
data, and fitted background expectations with error bars in all main regions.
This figure illustrates the background-model part of a \clown{likelihood}
function which is extended with signals to test alternative models.
Exclusion contours testing the addition of C1N2 and GMSB signals to these
backgrounds are shown in Figure~\ref{fig:2ljets_contours}.

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figures/2ljets_summary_log.pdf}
\caption{%
Data of the $\twoljets$ electroweak analysis with \emph{post-fit} backgrounds
for which the lower panel shows $S_\mathrm{ATLAS}$ from
Equation~\ref{eqn:significance_atlas}.
Control, validation and signal regions are shown from left to right, with the
regions within each category ordered approximately by their typical $\ptmiss$.
Likelihoods from validation regions are not included in the fit.
The `Top' category contains $t\bar t$ and $tW$ processes, and
`Other' contains fake/non-prompt lepton, higgs, triboson, $t\bar tZ$, and other
rare top processes.%
}
\label{fig:2ljets_summary}
\end{figure}

\begin{figure}[tp]
\centering
\begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/2ljets_contours_c1n2.pdf}
    \caption{C1N2 contours}
\end{subfigure}
\\[1em]
\begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=0.7\textwidth]{figures/2ljets_contours_gmsb.pdf}
    \caption{GMSB contours}
\end{subfigure}
\caption{%
Contours from the $\twoljets$ electroweak analysis for
C1N2 (top) and GMSB (bottom) models.
Space below the solid red line is labelled as excluded and its dotted
neighbours show the result if all signal cross-sections are varied up and down
by theoretical error bars.
The yellow band shows the prior $\pm1$-sigma region of exclusion contours
from asymptotic approximations to the distribution of the test statistic.
Grey areas are observed limits from the $2\ell$ parts
of~\cite{SUSY-2016-24} and~\cite{SUSY-2013-11}.
Exclusion is defined by the $\mathrm{CLs}$ prescription at the $0.05$ level
in asymptotic approximations.
All contours are interpolated from a sparse grid.
}
\label{fig:2ljets_contours}
\end{figure}
